%%% Hobbies
%%% ------------------------------------------------------------
\NewPart{Hobbies}{}

\WorkEntry
  {\href{https://github.com/nicholaswilde/cook-docs}{cook-docs}}
  {2022 -- Present}
  {}
  {A tool for automatically generating markdown documentation for cooklang recipes.}
\sepspace

\WorkEntry
  {\href{https://github.com/nicholaswilde/recipes}{Recipes}}
  {2022 -- Present}
  {}
  {A collection of recipes made with cooklang.}
\sepspace

\WorkEntry
  {Home Automation}
  {2012 -- Present}
  {}
  {Creating and managing a 40+ device smart home using a SmartThings hub and smart speakers. Protocols include ZigBee and Z-Wave.}
\sepspace

\WorkEntry
  {Home Networking}
  {2018 -- Present}
  {}
  {Creating and managing a network using UniFi hardware and software.}
\sepspace

\WorkEntry
  {\href{https://github.com/nicholaswilde/home-cluster}{Turing Pi Cluster}}
  {2020 -- 2022}
  {}
  {Managing a Turing Pi cluster using 7 RPi CM3+ running \textsc{k3s} on a Turing Pi 1.}
\sepspace

\WorkEntry
  {\href{https://github.com/nicholaswilde/helm-charts}{Helm Charts}}
  {2020 -- 2022}
  {}
  {A collection of helm charts.}
\sepspace

\WorkEntry
  {\href{https://github.com/search?q=user\%3Anicholaswilde+docker&type=Repositories}{Docker Images}}
  {2020 -- 2022}
  {}
  {A collection of multi-archicture Docker images.}
\sepspace

\WorkEntry
  {Traditional Woodworking}
  {2019 -- Present}
  {}
  {Using traditional woodworking hand tools such as planes, handsaw, hammers, and chisels to create Shaker style%
  \ furniture. Projects include a cherry side table, a cutting board, and English style workbench.}
\sepspace

\WorkEntry
  {Soccer}
  {2015 -- Present}
  {}
  {Play in an adult soccer league with 8 versus 8 on a smaller field. Also play pickup games twice a week with 10 to 20%
  \ other players.}
